Estimating the Number of Doctoral Degree Holders in the U.S.: A Comparative Analysis Using Laplace Ratio Estimators

### 2024-11-21 paper/state_respondents.qmd
refinement of subtitle

---
title: "Estimating the Number of Doctoral Degree Holders in the U.S.: A Comparative Analysis Using Laplace Ratio Estimators"
subtitle: "Discrepancy Between Estimated and Actual Totals Show Regional Variations in Educational Attainment"
author: 
  - Yunkyung Ko
  - YingKe He
  - Richard Guo
  - Ruikang Wang
  - Ziheng Zhong
thanks: "Code and data are available at: [https://github.com/koyunkyung/state_respondents](https://github.com/koyunkyung/state_respondents)."
date: today
date-format: long
abstract: "This paper uses the 2022 American Community Survey (ACS) data from IPUMS USA to estimate the total number of respondents with doctoral degrees across U.S. states using the Laplace ratio estimator. The estimated totals are compared to actual state-level respondent counts, highlighting discrepancies caused by regional variations in educational attainment. The results emphasize the limitations of applying a single ratio across diverse states and suggest that regional differences should be accounted for when using such estimation methods."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Estimating the Number of Doctoral Degree Holders in the U.S.: A Comparative Analysis Using Laplace Ratio Estimators"
subtitle: "Discrepancy Between Estimated and Actual Total Respondents Show Regional Variations in Educational Attainment"
author: 
  - Yunkyung Ko
  - YingKe He
  - Richard Guo
  - Ruikang Wang
  - Ziheng Zhong
thanks: "Code and data are available at: [https://github.com/koyunkyung/state_respondents](https://github.com/koyunkyung/state_respondents)."
date: today
date-format: long
abstract: "This paper uses the 2022 American Community Survey (ACS) data from IPUMS USA to estimate the total number of respondents with doctoral degrees across U.S. states using the Laplace ratio estimator. The estimated totals are compared to actual state-level respondent counts, highlighting discrepancies caused by regional variations in educational attainment. The results emphasize the limitations of applying a single ratio across diverse states and suggest that regional differences should be accounted for when using such estimation methods."
format: pdf
number-sections: true
bibliography: references.bib
---
